A pipeline to analyse time-course gene expression data

### 2020-06-05 scripts/manuscript.Rmd
another idea for fixing captions

```{r echo=FALSE, include=FALSE}
knitr::opts_chunk$set(
  cache=TRUE, autodep=TRUE, warning=FALSE, error=FALSE, message=FALSE,
  echo=TRUE, fig.width=4,
  duplicate.label="allow",out.extra = "")

>>>>

```{r echo=FALSE, include=FALSE}
knitr::opts_chunk$set(
  cache=TRUE, autodep=TRUE, warning=FALSE, error=FALSE, message=FALSE,
  echo=TRUE, fig.width=4,
  duplicate.label="allow",fig.align="center")
